### 2010-10-13 doc/tech_doc/a-rex/arex_tech_doc.tex
document new option for max jobs per DN

\item \textbf{\textit{maxjobs}}\textit{={[}max\_processed\_jobs {[}max\_running\_jobs]]}
-- specifies maximum number of jobs being processed by the A-REX at
different stages:\\

@@

processed by A-REX. This does not limit the amount of jobs, which can

@@

\textit{max\_running jobs} -- maximum number of jobs passed to Local

@@

>>>>

\item \textbf{\textit{maxjobs}}\textit{={[}max\_processed\_jobs
{[}max\_running\_jobs {[}max\_jobs\_per\_dn]]]} -- specifies maximum number of
jobs being processed by the A-REX at different stages:\\

@@

processed by A-REX. This does not limit the amount of jobs which can

@@

\textit{max\_running\_jobs} -- maximum number of jobs passed to Local

@@

\textit{max\_jobs\_per\_dn} -- maximum number of concurrent jobs processed by
A-REX per user DN. If this option is used the total maximum number of jobs
processed is still \textit{max\_processed\_jobs}.
\\ Missing value or -1 means no limit.
